---
title: "Submission"
author: "Jake Chanenson and Adriana Knight"
date: "5/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)      
library(ggplot2)      
library(colorspace)   #better colors for ggplot
library(tidyverse)    
library(dplyr)
library(gridExtra)
library(viridis)
library(ggridges)
library(broom)
library(stargazer)
library(corrr)
library(GGally)
library(RColorBrewer)
library(grid)
library(likert) # for creating a likert plot
library(kableExtra) # not needed but makes the table nicer
echoval <- F
load("../../Pew/pewTech.RData")
```


https://docs.google.com/document/d/1Omlr2cpmMBdgSE8haPFzKQSpPuO8OWO681qwiMvXYfk/edit

## Introduction 

Our physical and digital lives have been increasingly entwined during the first two decades of the twenty first century. A direct consequence of this entailment is the advent of what social psychologist Shoshana Zuboff calls "Surveillance Capitalism" – an economic model where a user’s personal data is commodified for profit generation. The commodification of personal data comes at the cost of user privacy as companies hoover up any and all quantifiable metrics about a given user. As such, it is now more important than ever to understand how the American people feel about issues surrounding the use of their data and their privacy. We choose two aspects of digital privacy to focus on: public sentiment surrounding right to be forgotten (RTBF) -- a privilege for people to remove photos, documents, and videos of themselves from public internet search -- and the privacy threat of Facial Recognition Technologies.    


## Key Figure 1

```{r RTBF, echo=echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others' information","Keep their own information private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49, fill = as.factor(sumRTBF))) +
  geom_bar(position = "dodge", color = 'black') +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Participants find it more important to...",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +
  scale_fill_brewer(palette="YlGnBu", name = "How many of the following\ncategories of data should\nfall under the Right To Be Forgotten:\n   -Data collected by law enforcement\n   -Employment history or work record\n   -Negative media coverage\n   -Potentially embarassing photos or\n     videos", labels=c("None","One","Two","Three","Four"))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```


### Explanation of Key Figure 1
BLAH BLAH BLAH BLAH.....
BLAH
BLAH
BLAH
BLAH BLAH 


## Key Figure 2

```{r FACE3, echo= echoval, message=FALSE}
#TODO: deal with POS fig.cap = "Key Figure 2", fig.pos = "!H"
###Data Manipulation###
## Create df of FACE3
df_f3 <- pew %>% filter(FACE3a_W49 != "No Answer" & FACE3b_W49 != "No Answer" & FACE3c_W49 != "No Answer") %>% filter(FACE3a_W49 != "Refused" & FACE3b_W49 != "Refused" & FACE3c_W49 != "Refused") %>%  dplyr::select(c(FACE3a_W49, FACE3b_W49, FACE3c_W49, groupKnow))

## Rename Cols
df_f3  <- df_f3  %>% 
  rename("Advertisers' Use Of Facial Recognition" = FACE3a_W49,
          "Tech Companies' Use Of Facial Recognition" = FACE3b_W49,
          "Law Enforcement's Use Of Facial Recognition" = FACE3c_W49)
df_f3  <- as.data.frame(df_f3)
df_f3 <- droplevels(df_f3) #remove unused levels 
df_f3 <- df_f3[, c(3,2,1,4)] #change order of cols for facets to come in nice order

## Reverse levels 
df_f3.reverse <- reverse.levels(df_f3)

                            
## Generate Title
title2 <- "Trust In Responsible Use Of Facial Recognition Tech\nFaceted on Tech Literacy"

###Data Viz###
## Centerd, No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```


### Explanation of Key Figure 2
BLAH BLAH BLAH BLAH.....
BLAH
BLAH
BLAH
BLAH BLAH 


\pagebreak


## Appdendix 

### Description of Dataset

The dataset we used is the 2019 PEW Survey on American Trends on Technology. The full citation for this data set
is as follows:

Pew Research Center. (2019). American Trends Panel (W49). Retrieved from https://www.dropbox.com/sh
/adyrtaju2jd7a2d/AAC2fmHoYs2SwVYKqCIkTxOsa?dl=0

The data set is a sample of 4272 respondents of people 18 years or older living in the US. This sample
consisted of both English and Spanish-language survey takers. The methodology also details the stratified
sampling. I have copied the statement from the methodology section below:

> The ATP subsample was selected by grouping panelists into seven stratum 1. Non-internet panelists. There were 691 total panelists in this stratum and they are sampled at a rate of 100% 2. HS or less panelists. There were 2,027 total panelists in this stratum and they are sampled at a rate of 98.9%. 2,005 panelists were selected for Wave 49. 3. Hispanic, Unregistered or Non-volunteers. There were 5,312 total panelists in this stratum and they are sampled at a rate of 44.8%. 2,380 panelists were selected for Wave 49. 4. Black or 18-34 panelists. There were 1,253 total panelists and they are sampled at a rate of 18.2%. 228 panelists were selected for Wave 49. 5. Other panelists. There were 4,176 total panelists and they are sampled at a rate of 13.5%. 564 panelists were selected for Wave 49.

#### Variables Used and Their Questions Phrasing


**Key Figure 1**

* `PUBLICDATA_W49` - "Today a wide range of information about people is searchable online. Do you think it is more important for people to have the ability to…"

* `RTBF` - "Do you think that ALL Americans should have the right to have the following information about themselves removed from public online search results?"

    - `RTBFa_W49` - "Data collected by law enforcement, such as criminal records or mugshots"
    
    - `RTBFb_W49` - "Information about their employment history or work record"
    
    - `RTBFc_W49` - "Negative media coverage"
    
    - `RTBFd_W49` - "Potentially embarrassing photos or videos"


**Key Figure 2**

* `FACE1` - "How much have you heard or read about the development of automated facial recognition technology that can identify someone based on a picture or video that includes their face?


* `FACE2` - "Based on what you know, how effective do you think facial recognition technology is at the following things?"
    
    - `FACE2a_W49` - "Accurately identifying individual people"  
    
    - `FACE2b_W49` - "Accurately assessing someone’s gender"  
        
    - `FACE2c_W49` - "Accurately assessing someone’s race" 
    
    
* `FACE3` - "How much, if at all, do you trust the following groups to use facial recognition technology responsibly?"
    
    - `FACE3a_W49` - "Advertisers"  
    
    - `FACE3b_W49` - "Technology companies"  
        
    - `FACE3c_W49` - "Law enforcement agencies" 
    
* `FACE4` - "In your opinion, is it acceptable or unacceptable to use facial recognition technology in the following situations?"
    
    - `FACE4a_W49` - "Law enforcement agencies assessing potential security threats in public spaces" 
    
    - `FACE4b_W49` - "Companies automatically tracking the attendance of their employees"  
        
    - `FACE4c_W49` - "Advertisers seeing how people respond to public advertising displays" 

    - `FACE4d_W49` - "Apartment building landlords tracking who enters or leaves their buildings"
    
* `KNOW1_W49` - "If a website uses cookies, it means that the site…

* `KNOW3_W49` - "When a website has a privacy policy, it means that the site… "

* `KNOW4_W49` - "What does it mean when a website has 'https://' at the beginning of its URL, as opposed to 'http://' without the 's'? "

* `KNOW7_W49` - "The term 'net neutrality' describes the principle that…"

* `KNOW8_W49` - "Many web browsers offer a feature known as 'private browsing' or 'incognito mode.' If someone opens a webpage on their computer at work using incognito mode, which of the following groups will NOT be able to see their online activities?"

* `KNOW9_W49` - "Some websites and online services use a security process known as two-step or two-factor authentication. Which of the following images is an example of two-factor authentication?"


* `CONCERNCO_W49` - "How concerned are you, if at all, about how companies are using the data they collect about you?"

### Additional Figures For Key Figure 1

### 1. Count Of PUBLICDATA Responses

```{r kf1-appendix-1, echo=echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others' information","Keep their own information private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49)) +
  geom_bar(fill="#47b7c3", color = 'black') +
  labs (
    title = "Count of PUBLICDATA Responses",
    subtitle = "Do you think it is more important for people to have the ability to...",
    x = "Responses",
    y = "Counts",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

### 2. How Much Data Do People Think We Have The Right To Forget?

```{r kf1-appendix-2, echo=echoval}
pew %>% drop_na(sumRTBF) %>% ggplot(aes(x = sumRTBF)) +
  geom_histogram(binwidth = 1, fill = "#a3d9b5") +
  labs (
    title = "Histogram of RTBF",
    subtitle = "How much do people think we have the right to forget?",
    x = "Number of acceptable categories to forget",
    y = "Count",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

### 3. Underlying Distribution Of Counts For All Four RTBF Categories

```{r kf1-appendix-3, echo=echoval}

levels(pew$RTBFa_W49) <- c("Should be forgotten","Should be remembered", "Refused")
p1 <- pew %>% drop_na(RTBFa_W49) %>% filter(RTBFa_W49 != "Refused") %>% ggplot(aes(x = RTBFa_W49)) +
      geom_bar(fill = "#47b7c3", color = 'black') +
      labs (
      title = "Right To Be Forgotten (A)",
      subtitle = "Data collected by law enforcement"
      ) + theme(axis.title.x=element_blank(), axis.title.y=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"))

levels(pew$RTBFb_W49) <- c("Should be forgotten","Should be remembered", "Refused")
p2 <- pew %>% drop_na(RTBFb_W49) %>% filter(RTBFb_W49 != "Refused") %>% ggplot(aes(x = RTBFb_W49)) +
      geom_bar(fill = "#47b7c3", color = 'black') +
      labs (
      title = "Right To Be Forgotten (B)",
      subtitle = "Employment history or work record"
      ) + theme(axis.title.x=element_blank(), axis.title.y=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"))

levels(pew$RTBFc_W49) <- c("Should be forgotten","Should be remembered", "Refused")
p3 <- pew %>% drop_na(RTBFc_W49) %>% filter(RTBFc_W49 != "Refused") %>% ggplot(aes(x = RTBFc_W49)) +
      geom_bar(fill = "#47b7c3", color = 'black') +
      labs (
      title = "Right To Be Forgotten (C)",
      subtitle = "Negative media coverage"
      ) + theme(axis.title.x=element_blank(), axis.title.y=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"))

levels(pew$RTBFd_W49) <- c("Should be forgotten","Should be remembered", "Refused")
p4 <- pew %>% drop_na(RTBFd_W49) %>% filter(RTBFd_W49 != "Refused") %>% ggplot(aes(x = RTBFd_W49)) +
      geom_bar(fill = "#47b7c3", color = 'black') +
      labs (
      title = "Right To Be Forgotten (D)",
      subtitle = "Potentially embarrassing photos or videos"
      ) + theme(axis.title.x=element_blank(), axis.title.y=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"))

grid.arrange(p1,p2,p3,p4, 
             ncol=2,
            top = textGrob("Underlying Distribution Of Counts For All Four RTBF Categories",
              x = 0, # need to keep on left
              y = .7,
              just = "left", #left justified
              gp = gpar(fontsize = 18) # bigger font
             ),
             bottom = textGrob("Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy",
                               x = 1, #is on domian [0,1]
                               gp = gpar(fontsize = 8), # smaller font
                           just = "right") #right justified
            ) 
```

### Additional Figures For Key Figure 2



### 1. Underlying Distribution of Tech Literacy


```{r KNOW-Counts, echo=echoval, out.height="50%"}
pew %>% ggplot(aes(x =sumKnowFactor, fill = groupKnow)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Distribution of Tech Literacy Scores",
    subtitle = "How Many Out Of The Six Tech Literacy Questions Did Respondents Get Correct",
    y = "Counts",
    x = "Literacy Category",
    fill = "Respondent's\nLiteracy Score",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```




### 2. Self Reported Facial Recognition Familiarity

```{r FACE2_Bar, echo=echoval, message=FALSE}
pew %>% filter(FACE1_W49 != "Refused") %>% ggplot(aes(x = groupKnow, fill = FACE1_W49)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Respondent's Self Reported Familiarity With Facial Recognition",
    y = "Counts",
    x = "Literacy Category",
    fill = "How Much The Respondent\nKnows About Facial Recognition",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

### 3. Respondent's Understanding of Facial Recognition 
```{r FACE3_Likert, echo=echoval, message=FALSE}
###Generate the Data Frame###
## Create df of FACE2
df_f2 <- pew %>% filter(FACE2a_W49 != "Refused" & FACE2b_W49 != "Refused" & FACE2c_W49 != "Refused") %>%  dplyr::select(c(FACE2a_W49, FACE2b_W49, FACE2c_W49, groupKnow))

## Rename Cols
df_f2  <- df_f2  %>% 
  rename("Accurately identifying individual people" = FACE2a_W49,
          "Accurately assessing someone’s gender" = FACE2b_W49,
          "Accurately assessing someone’s race" = FACE2c_W49)
df_f2  <- as.data.frame(df_f2)
df_f2 <- droplevels(df_f2) #remove unused levels 
# df_f2 <- df_f2[, c(3,2,1,4)] #change order of cols for facets to come in nice order

## Reverse levels 
df_f2.reverse <- reverse.levels(df_f2)

                            
## Generate Title
titlef2 <- "How Effective Do Respondents Think Facial Recognition Is\nFaceted on Tech Literacy"

###Graph The Likert Data###
plot(likert(df_f2.reverse[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f2[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```


### 4. What Situations Respondent Think It Is Acceptable To Use Facial Recognition

```{r FACE4_Likert, echo=echoval, message=FALSE}
df_f4 <- pew %>% select(c(FACE4a_W49, FACE4b_W49, FACE4c_W49, FACE4d_W49, groupKnow))

df_f4 <- df_f4 %>% 
  rename("Law Enforcement Assesing Threats In Public Spaces" = FACE4a_W49,
          "Companies Tracking Employee Attendance" = FACE4b_W49,
          "Advertisers Measuring Responses To Public Displays" = FACE4c_W49,
          "Lanlords Tracking Who Enters and Leaves Their Building" = FACE4d_W49)
df_f4 <- as.data.frame(df_f4)
df_f4 <- droplevels(df_f4, exclude = c("Refused", "Not sure", "NA", "<NA>")) #remove unused levels
df_f4 <- droplevels(df_f4)

## Reverse levels 
df_f4.reverse <- reverse.levels(df_f4)
df_f4.reverse2 <- reverse.levels(df_f4.reverse) #R wackyness reverse takes away NA so to get fd_f4 without NA we need to reverse the reverse

titlef4 <- "Opinions on Facial Recognition Use Faceted on Tech Litercay"

###Graph The Likert Data###
plot(likert(df_f4.reverse[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 1.5) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f4.reverse2[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", centered = FALSE, plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE,) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

### Additional Tables For Key Figure 1

```{r KF1-tables, echo=echoval}
#Simple simple table of counts
KF1_T1 <- table(pew$sumRTBF, pew$publicDataNum) #public data should be private = 0
colnames(KF1_T1) = c("Data Should Be Private","Data Should Be Public")

KF1_T1 <- as.data.frame(KF1_T1)

KF1_T1 <- KF1_T1 %>% rename(
  "sumRTBF" = "Var1",
  "Stance On RTBF" = "Var2",
)

#Table showing summary of sumRTBF var across publicData = 0 (private) and 1 (public)
public_grouped_data <- pew %>%
  group_by(publicDataNum)

KF1_T2 <- public_grouped_data %>% drop_na(sumRTBF) %>% summarize(
  mean=mean(sumRTBF, na.rm=TRUE),
  sd=sd(sumRTBF, na.rm=TRUE)
)

##Render Tables
knitr::kable(KF1_T1, "simple", caption = "Summary Statistics For Key Figure 1")
knitr::kable(KF1_T2 , "simple", caption = "Numeric Summary That Involves Uncertainty For Key Figure 1")

```

### Additional Tables For Key Figure 2

```{r KF2-tables, echo=echoval}
KF2_T <- summary(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]))
KF2_T1 <- KF2_T[, c(1,2,3,5,6)] # remove neutral column b/c it isn't relevant
KFT_T2 <- KF2_T[, c(1,2,6,7)] # remove neutral column b/c it isn't relevant

##Render Tables
knitr::kable(KF2_T1, "simple", caption = "Summary Statistics For Key Figure 2")
knitr::kable(KFT_T2, "simple", caption = "Numeric Summary That Involves Uncertainty For Key Figure 2")
```

### Discussion of Uncertainty & Inference

**Key Figure 1**

**Key Figure 2**

### Discussion of Analytic  Choices

Our analytical choices, while earnestly centered around most accurately representing the “truth,” are imperfect. We will proceed with an explanation and critique of our analytical choices using Pierre Bourdieu’s “Public Opinion Does Not Exist” and chapters 1 and 8 of *Data Visualization: A Practical Introduction* by Kieran Healy. 

Per Pierre Bourdieu’s article “Public Opinion Does Not Exist,” our primary critique of the analytic choices that both we and the source of our data set (the Pew Research Center) made is that we are relying heavily on the survey data yielded by the 2019 Pew American Trends Panel survey as being accurately representative of “the public.”

First, to echo Bourdieu’s writings, we would like to problematize our use of the idea of “the public” at all; the data we have been manipulating, and the visualizations produced therein, are by no means necessarily representative of “the public.” The public, as we would like to think of it, does not exist. Per the topline we received as part of this data set, the *actual* body of people surveyed is 5,869 members of the American Trends Panel: a national, probability-based online panel of non-institutionalized adults living in households in the United States, including Alaska and Hawaii. The fact that this is a pre-selected, probability-based panel highlights that the body of participants does not encompass every single person living in the United States, nor does every person living in the United States who interacts in some meaningful way with technology and digital privacy fall under those categorizations. Pew Research Center is a meticulous, thorough group known for producing robust data as well as analyses of said data. Though, there will always be blind spots, which we must be mindful of when discussing* what* exactly our work produced.

In that regard we are guilty, also, of using this data as a means of making some grand statement about the status of society as a means of gauging “where we are” in regard to digital privacy. Bourdieu writes that “[the public opinion poll] creates the idea that a unanimous public opinion exists in order to legitimate a policy, and strengthen the relations of the force upon which it is based or make it possible” (Bourdieu 125). Not every person has or is even *able* to produce an opinion on every single question posed by the survey; this much is proved by the sheer volume of NAs in response to certain questions. We also do not know *what* those NAs even mean; Bourdieu defines the “consensus effect” to be the tendency to overlook the proportion of respondents who gave “no reply” homogenizes the populus and ignores the political reasons for certain demographics to not respond depending on the variety of question. We do not know, truly, what those NAs mean; we made the decision to largely strike them from our visualizations to help tell a better story, but that narrative in turn excludes some body whose voices we neither know nor understand, which could in turn shift our general understanding of the field of digital privacy as a whole. 

The last point of contention or concern within our analysis of our data is the constantly shifting landscape of digital literacy as a whole. We are still only a few mere decades into the digital age, meaning that there is a notable generational gap in literacy, skill sets, and general understanding of the tools offered and threats posed by the digital sphere. One of our visuals does aim to gauge technical literacy, using a dummy summary count variable, though we are cautious to take it as the unchallenged truth. For those and other variables, respondents may feign understanding of topics, or answer in line to how they think they should. As such, we can at best be only cautiously optimistic about the results our analyses yield, knowing that our variables are at best approximations, and we are representing not the hypothetical, homogenous “public” but rather a pre-selected sample group.

Moving into our *visual* analyses, we turn to Healy, particularly the ideals outlined within chapters 1 and 8. Based on those readings, we took great pain thinking about presentation and accessibility in our design. The primary sins of bad design, as Healy describes them, are bad taste, bad perception, and bad data. We have done our best to address the source of data for analysis already above, and by no means cherry picked our data to further a narrative that we would prefer to tell over the one the data produced with our manipulations. For the first two, we have done our best to present the information in as clear and concise a way as we could manage. Leaning into ideas from chapter 8, we wanted to maintain not only high quality of visuals (no wasted ink, clear and regular visuals) but also accessibility. We used pre-built color palettes to display our data - sequential color palettes for unordered categorical data and diverging color palettes for ordered categorical data. In addition, it was important that we make sure our visuals were widely accessible by identifying color-blind friendly palates in colorbrewer via `display.brewer.all(colorblindFriendly = TRUE)` to select palettes that would work even for those with different abilities or perceptions. Our goal was to keep our color palette and our visual decisions at large consistent with the underlying data, visually pleasing, and accessible to all.


### Discussion Of Other Ways We Could Have Made Our Key Figure

**Key Figure 1**

BLAH BLAH BLAH

```{r central_fig, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("Find Others' Information","Keep Their Own Information Private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = sumRTBF, fill = as.factor(sumRTBF))) +
  geom_bar(position = "dodge", color= 'black') +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Count of How Many Categories Participants Identified to Fall\nUnder the Right To Be Forgotten",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +
  scale_fill_brewer(palette="YlGnBu") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.position = "none") + 
  facet_wrap(~PUBLICDATA_W49)
```


**Key Figure 2**

When visualizing my key figure, I knew that I wanted to visualize some form of stacked bar chart to communicate the relative differences in comfort of various groups using facial recognition technology. Professor Ella Foster-Molina sent me an excellent article from Datawrapper making the case against diverging stacked bar charts and offering 100% bar charts as the better alternative. The article argues that “the main problem with diverging bars, however, is comparability.” On the whole, I agree; to me, the most compelling point of the piece relates to how neutrals are handled in the diverging stacked bar charts. Putting neutrals in the middle means that (1) none of the bars have a common baseline and (2) the chart is implying that part of the neutrals should be coded as positive and negative respectively. 
That all being said, none of my charts have neutrals. Thus, I think the diverging bar chart looks just fine because the overall positive-negative trend both within and between facets is more pronounced. Below is what the figure would look like with a 100% bar chart.   

```{r FACE3 Alt, echo=echoval, message=FALSE}
## 100% BarPlot
plot(likert(df_f3[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```


### Distribution of Work

Jake and Adriana are best of friends and have split the work evenly. [PLACEHOLDER].

```{r, echo=F, message=FALSE}

```

